---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/musicbrainz)](http://cran.r-project.org/package=musicbrainz)


# musicbrainz

The goal of musicbrainz is to make it easy to call the MusicBrainz Database API from R.

## Installation

You can install musicbrainz from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("dmi3kno/musicbrainz")
```

## Example

There are three families of functions in `musicbrainz` package: search, lookup and browse.

### Search

Lets search information about Miles Davis

```{r miles}
library(musicbrainz)
library(dplyr)

miles_df <- search_artists("Miles Davis")
miles_df
```

It looks like the first hit is what we need. We can use `dplyr` to extract the information of interest

```{r id}
miles_id <- miles_df %>% 
  select(mbid) %>%
  slice(1) %>% 
  pull()
```

### Lookup

Now that we have MusicBrainz id ("mbid") we can call the lookup function.

```{r lookup}
miles_lookup <- lookup_artist_by_id("561d854a-6a28-4aa7-8c99-323e6ce46c2a")
miles_lookup
```

### Browse

We can also browse linked records (such as all releases by Miles Davis).

```{r browse}
miles_releases <- browse_releases_by("artist", "561d854a-6a28-4aa7-8c99-323e6ce46c2a")
miles_releases
```
