---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/musicbrainz)](http://cran.r-project.org/package=musicbrainz)


# musicbrainz

The goal of musicbrainz is to make it easy to call the MusicBrainz Database API from R. Currently API does NOT require authentication for reading the data, however, requests to the database are subject to a rate limit of 1 request/sec. The package utilizes `ratelimitr` to make sure you don't need to worry about exceeding that limit.  

## Installation

You can install musicbrainz from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("dmi3kno/musicbrainz")
```

## Example

There are three families of functions in `musicbrainz` package: search, lookup and browse.

### Search

Lets search information about Miles Davis

```{r miles}
library(musicbrainz)
library(dplyr)

miles_df <- search_artists("Miles Davis")
miles_df
```

It looks like the first hit is what we need. We can use `dplyr` to extract the information of interest

```{r id}
miles_id <- miles_df %>% 
  select(mbid) %>%
  slice(1) %>% 
  pull()
```

### Lookup

Now that we have MusicBrainz id ("mbid") we can call the lookup function.

```{r lookup}
miles_lookup <- lookup_artist_by_id("561d854a-6a28-4aa7-8c99-323e6ce46c2a")
miles_lookup
```

### Browse

We can also browse linked records (such as all releases by Miles Davis).

```{r browse}
miles_releases <- browse_releases_by("artist", "561d854a-6a28-4aa7-8c99-323e6ce46c2a")
miles_releases
```

## References
 
 1. Details of the Musicbrainz database API: https://musicbrainz.org/doc/Development/XML_Web_Service/Version_2
 2. Details about rate limits: https://musicbrainz.org/doc/XML_Web_Service/Rate_Limiting
